---
title: "How Do Penguin Species Differ?"
author: "David Zhang"
date: "2026-09-22"
---

## Introduction

Brief intro of the question and dataset goes here.

Data: [Palmer Penguins](https://allisonhorst.github.io/palmerpenguins/), Gorman KB, Williams TD, Fraser WR (2014). Palmer Station Antarctica LTER / palmerpenguins R package. CC0 license.

## Setup

```{r}
#| message: false
#| warning: false
library(palmerpenguins)
library(tidyverse)
```

## Wrangling

```{r}
penguins_clean <- penguins |> 
  drop_na()

glimpse(penguins_clean)
```

## Summary Statistics

```{r}
penguins_clean |> 
  group_by(species, island) |> 
  summarize(
    mean_mass = mean(body_mass_g),
    mean_flipper = mean(flipper_length_mm),
    n = n(),
    .groups = "drop"
  )
```

## Figure

```{r}
#| label: fig-penguin-mass
#| fig-cap: "Flipper length vs. body mass by species."
ggplot(penguins_clean, aes(x = flipper_length_mm, y = body_mass_g, color = species)) +
  geom_point(alpha = 0.7, size = 2) +
  labs(
    x = "Flipper length (mm)",
    y = "Body mass (g)",
    color = "Species"
  ) +
  theme_minimal()
```

## Findings

Through this analysis we find that body mass and flipper length differ largely by species but do not differ much when it comes to what island they reside on. Adelie penguins have a consistent mean body mass around 
3700g regardless of Island. Chinstrap penguins are close to Adelie in size, at roughly 3733g on average.

Gentoo penguins stand apart. With a mean body mass of about 5092g and mean 
flipper length of 217mm, they are noticeably heavier and longer-flippered 
than either Adelie or Chinstrap. They are roughly 1.4kg heavier on average than Adelie. 

We see the same results showcased in our figure with Gentoo penguins clearly being on the upper right section of the grpah corresponding to higher body mass and flipper length.